### 2021-06-10 paper/report.tex
Work on first batch of comments in report.tex.

The model includes several other features, which are crucial to describe the evolution
of the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness can be introduced. Agents may receive a vaccination. With a probability
of 75\% \citep{Hunter2021}, vaccinated agents become immune and they do not transmit the
virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.\comment[id=T]{Maybe add
that 35\% reach immunity after two weeks and 40\% after three weeks.}\footnote{75\% is
    lower than what is usually reported for after the second dose of the Biontech/Pfizer
    vaccine, which is most commonly used in Germany. We choose it because our model neither
    includes booster shots, nor does it allow vaccinated individuals who became immune to
    transmit the disease\citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}. If
    anything, these assumptions would overstate the effect of vaccines for our study period.
    This would be different if a large fraction of vaccinated individuals had received a
    second dose already.} During the vaccine roll-out, priority may depend on age and
occupation.

We include two types of tests. Polymerase chain reaction (PCR) tests directly reveal
whether an individual is infected or not. PCR tests require some days to be processed
and there are aggregate capacity constraints throughout. In contrast, rapid antigen
tests yield immediate results; after a phase-in period, all tests that are demanded will
be performed. Specificity and sensitivity of these tests is set according to data
analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of the
test relative to the start of infectiousness. Figure~\ref{fig:antigen_tests} shows our
model for rapid test demand. Schools may require students to be tested regularly. Rapid
tests may be offered by employers for on-site workers. Individuals may demand tests for
private reasons, which include having plans to meet other people\footnote{A positive
    test will make them reduce their contacts; this is why tests impact the actual contacts
    in Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and because a
household member tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid tests offered
by employers or follows up on private reasons. The thresholds are lower for tests in a
private setting than for tests at the workplace.\comment[id=HM]{True? @Janos}

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\comment[id=HM]{
% \footnote{
See section S.XXX of the supplementary materials for an overview.
% }
} Mobility data is used to model the reductions in work contacts. School and daycare
policies can be incorporated directly from official directives. Aggregate tests,
vaccinations, and the prevalence of virus strains can be taken from official records and
from survey data.\comment[id=HM]{Anything else we need to mention?} We estimate the
infection probabilities\comment[id=HM]{need to be more precise here, cannot find in
Appendix} that the simulated new infections predict age- and region-specific time
series. However, the two sets of time series are not comparable directly because not all
cases will be recorded. We model the fraction of recorded cases as depicted in
Figure~\ref{fig:model_for_official_cases}.\comment[id=HM]{Add a sentence.}

>>>>

The model includes several other features, which are crucial to describe the evolution
of the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness can be introduced. Agents may receive a vaccination. With a probability
of 75\% \citep{Hunter2021}, vaccinated agents become immune and they do not transmit the
virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.\footnote{75\% is
    lower than what is usually reported for after the second dose of the Biontech/Pfizer
    vaccine, which is most commonly used in Germany. We choose it because our model neither
    includes booster shots, nor does it allow vaccinated individuals who became immune to
    transmit the disease\citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}. If
    anything, these assumptions would overstate the effect of vaccines for our study period.
    This would be different if a large fraction of vaccinated individuals had received a
    second dose already.} During the vaccine roll-out, priority may depend on age and
occupation.

We include two types of tests. Polymerase chain reaction (PCR) tests directly reveal
whether an individual is infected or not. PCR tests require some days to be processed and
there are aggregate capacity constraints throughout. In contrast, rapid antigen tests
yield immediate results; after a phase-in period, all tests that are demanded will be
performed. Specificity and sensitivity of these tests is set according to data analyzed
in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of the test relative
to the start of infectiousness. Figure~\ref{fig:antigen_tests} shows our model for rapid
test demand. Schools may require students to be tested regularly. Rapid tests may be
offered by employers for on-site workers. Individuals may demand tests for private
reasons, which include having plans to meet other people\footnote{A positive test will
make them reduce their contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and because a
household member tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid tests offered
by employers or follows up on private reasons and whether she reduces her contacts if she
tests positive or develops symptoms. The thresholds are higher for tests in a private
setting than for tests at the workplace until mid April and then compliance because of
private reasons becomes higher than compliance at the workplace.

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section~\ref{sec:data_and_parameters} of the supplementary
materials for an overview.} We can rely on contact diaries to get pre-pandemic
distributions of contacts for different contact types and their assortativity by age
group. Mobility data is used to model the reductions in work contacts. School and daycare
policies can be incorporated directly from official directives. Aggregate tests,
vaccinations and the prevalence of virus strains can be taken from official records. The
likelihood to receive a test offer or to take up a test offer and the share of
individuals that have ever taken a test or done weekly tests in the last month can be
calibrated from survey data.\comment[id=HM]{Anything else we need to
mention?}\comment[id=K]{I added some more that I think are worth mentioning.} We estimate
the infection probabilities\comment[id=HM]{need to be more precise here, cannot find in
Appendix}\comment[id=K]{I added \ref{subsec:infection_probs}.} that the simulated new
infections predict age- and region-specific time series.\comment[id=K]{We never directly
targeted the federal states if I remember it right. How large was their weight in the
criterion function @Janos?} However, the two sets of time series are not comparable
directly because not all cases will be recorded. We model the fraction of recorded cases
as depicted in Figure~\ref{fig:model_for_official_cases}.\comment[id=HM]{Add a sentence.}
